---
title: "linear model"
output: html_document
---

```{r setup, include=FALSE}
source("../_harness/use_r_codecarbon.R")
use_r_codecarbon()
```

## Workload

A short-running, CPU-only, small in-memory statistical modeling case: fit
a multiple linear regression on synthetic data (50,000 rows, 10 predictors)
with `lm()`, paired against `sklearn.linear_model.LinearRegression` in
Python. `sklearn` rather than `statsmodels` since it's already a dependency
of case 01's environment; `LinearRegression` is an ordinary-least-squares
fit like `lm()`, so this is a direct analog rather than a different
estimation method.

The predictors and response are generated once (below) and written to
`shared_data.csv`, which both chunks read, rather than each side
generating its own with a matching seed -- R's and Python's RNGs aren't
bit-compatible, so "the same" seed wouldn't actually produce the same
values. `shared_data.csv` is generated fresh on every render and
gitignored.

## Shared data

```{r}
set.seed(42)
n <- 50000
p <- 10
x <- matrix(rnorm(n * p), nrow = n)
colnames(x) <- paste0("x", seq_len(p))
beta <- rnorm(p)
y <- as.vector(x %*% beta + rnorm(n, sd = 2))
shared <- as.data.frame(x)
shared$y <- y
write.csv(shared, "shared_data.csv", row.names = FALSE)
```

## R run

```{r}
library(CodeCarbonR)

data <- read.csv("shared_data.csv")

result <- with_emissions_tracked(
  {
    fit <- lm(y ~ ., data = data)
    summary(fit)$r.squared
  },
  country_iso_code = "USA",
  output_dir = "r_output"
)

cat("R-squared:", round(result$result, 4), "\n")
result
```

## Python run

```{python}
import os
import pandas as pd
from sklearn.linear_model import LinearRegression
from codecarbon import OfflineEmissionsTracker

os.makedirs("py_output", exist_ok=True)

data = pd.read_csv("shared_data.csv")
feature_cols = [c for c in data.columns if c != "y"]
X = data[feature_cols]
y = data["y"]

with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
    model = LinearRegression()
    model.fit(X, y)
    r_squared = model.score(X, y)

print(f"R-squared: {r_squared:.4f}")
```

## Comparison

```{r}
source("../_harness/compare_emissions.R")
compare_emissions(".")
```
