---
title: "random forest classification"
format: html
---

## Workload

Train a random forest classifier on a synthetic dataset (1000 rows, 20
features), mirroring CodeCarbon's own scikit-learn documentation example:
https://docs.codecarbon.io/latest/how-to/scikit-learn/. This is the primary
accuracy calibration case, since it's the closest direct analog between the
two languages.

Caveat: R's `ranger` and Python's `RandomForestClassifier` are different
implementations and won't take identical wall-clock time even on
equivalent data, so this validates that CodeCarbonR's reported numbers are
in a sane range proportional to actual CPU work, not that duration matches
exactly between the two runs. The synthetic data is also not bit-identical
between languages (R doesn't have a drop-in equivalent of sklearn's
`make_classification`); both use 1000 rows x 20 features with a
linear-combination-plus-noise labeling rule.

## R run

```{r}
library(CodeCarbonR)
library(ranger)

set.seed(42)
n <- 1000
p <- 20
x <- matrix(rnorm(n * p), nrow = n)
beta <- rnorm(p)
linpred <- x %*% beta
y <- factor(ifelse(linpred + rnorm(n) > median(linpred), 1, 0))
data <- as.data.frame(x)
data$y <- y

train_idx <- sample(seq_len(n), size = 0.8 * n)
train_data <- data[train_idx, ]
test_data <- data[-train_idx, ]

result <- with_emissions_tracked(
  {
    model <- ranger(y ~ ., data = train_data, num.trees = 100)
    predictions <- predict(model, test_data)$predictions
    mean(predictions == test_data$y)
  },
  country_iso_code = "USA",
  output_dir = "r_output"
)

cat("Model accuracy:", round(result$result, 3), "\n")
result
```

## Python run

```{python}
from sklearn.datasets import make_classification
from sklearn.model_selection import train_test_split
from sklearn.ensemble import RandomForestClassifier
from codecarbon import OfflineEmissionsTracker

X, y = make_classification(n_samples=1000, n_features=20, random_state=42)
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2)

with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
    model = RandomForestClassifier(n_estimators=100, random_state=42)
    model.fit(X_train, y_train)
    accuracy = model.score(X_test, y_test)

print(f"Model accuracy: {accuracy:.3f}")
print(f"Training emissions: {tracker.final_emissions:.6f} kg CO2eq")
```

## Comparison

```{r}
source("../_harness/compare_emissions.R")
compare_emissions(".")
```
