---
title: "random forest classification"
output: html_document
---

```{r setup, include=FALSE}
reticulate::use_condaenv("r-codecarbon", required = TRUE)
```

## Workload

Train a random forest classifier on a synthetic dataset (1000 rows, 20
features), mirroring CodeCarbon's own scikit-learn documentation example:
https://docs.codecarbon.io/latest/how-to/scikit-learn/. This is the primary
accuracy calibration case, since it's the closest direct analog between the
two languages.

R's `ranger` and Python's `RandomForestClassifier` are still different
implementations and won't take identical wall-clock time on identical
data -- that part of the comparison validates that CodeCarbonR's reported
numbers are in a sane range proportional to actual CPU work, not that
duration matches exactly between the two runs.

What *is* identical: the data and the train/test split. The block below
generates the features, labels, and an `is_train` split assignment once,
writes them to `shared_data.csv`, and both the R and Python chunks read
that same file rather than each generating their own (R doesn't have a
drop-in equivalent of sklearn's `make_classification`, and even with
matching seeds R's and Python's RNGs don't produce the same values from
them). This removes "is the data actually the same" as a variable, so any
remaining divergence in reported numbers is attributable to the R vs.
Python implementations and runtimes, not to the two sides quietly working
from different inputs. `shared_data.csv` is generated fresh on every
render and gitignored, not checked into the repo.

## Shared data

```{r}
set.seed(42)
n <- 1000
p <- 20
x <- matrix(rnorm(n * p), nrow = n)
beta <- rnorm(p)
linpred <- x %*% beta
y <- as.integer(ifelse(linpred + rnorm(n) > median(linpred), 1, 0))
train_idx <- sample(seq_len(n), size = 0.8 * n)
is_train <- as.integer(seq_len(n) %in% train_idx)

shared <- as.data.frame(x)
names(shared) <- paste0("x", seq_len(p))
shared$y <- y
shared$is_train <- is_train
write.csv(shared, "shared_data.csv", row.names = FALSE)
```

## R run

```{r}
library(CodeCarbonR)
library(ranger)

shared <- read.csv("shared_data.csv")
shared$y <- factor(shared$y)
train_data <- shared[shared$is_train == 1, setdiff(names(shared), "is_train")]
test_data <- shared[shared$is_train == 0, setdiff(names(shared), "is_train")]

result <- with_emissions_tracked(
  {
    model <- ranger(y ~ ., data = train_data, num.trees = 100)
    predictions <- predict(model, test_data)$predictions
    mean(predictions == test_data$y)
  },
  country_iso_code = "USA",
  output_dir = "r_output"
)

cat("Model accuracy:", round(result$result, 3), "\n")
result
```

## Python run

```{python}
import os
import pandas as pd
from sklearn.ensemble import RandomForestClassifier
from codecarbon import OfflineEmissionsTracker

os.makedirs("py_output", exist_ok=True)
shared = pd.read_csv("shared_data.csv")
feature_cols = [c for c in shared.columns if c not in ("y", "is_train")]
train = shared[shared["is_train"] == 1]
test = shared[shared["is_train"] == 0]
X_train, y_train = train[feature_cols], train["y"]
X_test, y_test = test[feature_cols], test["y"]

with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
    model = RandomForestClassifier(n_estimators=100, random_state=42)
    model.fit(X_train, y_train)
    accuracy = model.score(X_test, y_test)

print(f"Model accuracy: {accuracy:.3f}")
print(f"Training emissions: {tracker.final_emissions:.6f} kg CO2eq")
```

## Comparison

```{r}
source("../_harness/compare_emissions.R")
compare_emissions(".")
```
