---
title: "large csv io"
output: html_document
---

```{r setup, include=FALSE}
reticulate::use_condaenv("r-codecarbon", required = TRUE)
```

## Workload

TODO: the large-file / I/O-bound case. Generate, write, read back, and
aggregate a large CSV (target ~1 GB) to exercise disk I/O and rule out
platform-specific file path or I/O handling bugs (this is the case most
likely to expose Windows vs. Linux vs. Mac path issues). Needs a decision
on whether the generated file is checked into the repo (no, too large),
generated fresh each run, or downloaded from a fixed source.

## R run

```{r}
# library(CodeCarbonR)
#
# result <- with_emissions_tracked(
#   {
#     # write large CSV, read it back, aggregate
#   },
#   country_iso_code = "USA",
#   output_dir = "r_output"
# )
```

## Python run

```{python}
# from codecarbon import OfflineEmissionsTracker
#
# with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
#     pass  # equivalent write/read/aggregate
```

## Comparison

```{r}
# source("../_harness/compare_emissions.R")
# compare_emissions(".")
```
