---
title: "large csv io"
output: html_document
---

```{r setup, include=FALSE}
reticulate::use_condaenv("r-codecarbon", required = TRUE)
```

## Workload

The large-file / I/O-bound case: generate an in-memory table, write it to
disk as CSV (target ~1 GB), read it back, and aggregate it. Exercises disk
I/O specifically, to rule out platform-specific file path or I/O handling
bugs (this is the case most likely to expose Windows vs. Linux vs. Mac
path issues, though only Windows and Linux are validated so far -- see
`../coverage_matrix.md`).

The generated file is never checked into the repo: it's written fresh into
`r_output/`/`py_output/` (already gitignored) on every render and deleted
at the end of the chunk, after tracking stops. R uses `readr` for
write/read (base `write.csv`/`read.csv` would make this case take several
times longer without meaningfully changing what it validates); Python uses
pandas, consistent with the other cases in this suite.

## R run

```{r}
library(CodeCarbonR)
library(readr)
library(dplyr)

set.seed(42)
n <- 18000000
categories <- c("alpha", "beta", "gamma", "delta", "epsilon", "zeta")
csv_path <- file.path("r_output", "large_data.csv")

result <- with_emissions_tracked(
  {
    data <- data.frame(
      id = seq_len(n),
      category = sample(categories, n, replace = TRUE),
      value_a = round(rnorm(n), 4),
      value_b = round(runif(n, -100, 100), 4),
      value_c = round(rexp(n), 4),
      flag = sample(c(TRUE, FALSE), n, replace = TRUE)
    )
    write_csv(data, csv_path)
    rm(data)

    loaded <- read_csv(csv_path, show_col_types = FALSE)
    loaded %>%
      group_by(category) %>%
      summarise(
        n = n(),
        mean_a = mean(value_a),
        mean_b = mean(value_b),
        mean_c = mean(value_c),
        .groups = "drop"
      )
  },
  country_iso_code = "USA",
  output_dir = "r_output"
)

file_size_mb <- file.size(csv_path) / 1024^2
cat("CSV size:", round(file_size_mb, 1), "MB\n")
print(result$result)
unlink(csv_path)
result
```

## Python run

```{python}
import os
import numpy as np
import pandas as pd
from codecarbon import OfflineEmissionsTracker

os.makedirs("py_output", exist_ok=True)
np.random.seed(42)
n = 18_000_000
categories = ["alpha", "beta", "gamma", "delta", "epsilon", "zeta"]
csv_path = os.path.join("py_output", "large_data.csv")

with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
    data = pd.DataFrame({
        "id": np.arange(1, n + 1),
        "category": np.random.choice(categories, n),
        "value_a": np.round(np.random.normal(size=n), 4),
        "value_b": np.round(np.random.uniform(-100, 100, n), 4),
        "value_c": np.round(np.random.exponential(size=n), 4),
        "flag": np.random.choice([True, False], n),
    })
    data.to_csv(csv_path, index=False)
    del data

    loaded = pd.read_csv(csv_path)
    summary = loaded.groupby("category").agg(
        n=("id", "size"),
        mean_a=("value_a", "mean"),
        mean_b=("value_b", "mean"),
        mean_c=("value_c", "mean"),
    )

file_size_mb = os.path.getsize(csv_path) / 1024**2
print(f"CSV size: {file_size_mb:.1f} MB")
print(summary)
os.remove(csv_path)
```

## Comparison

```{r}
source("../_harness/compare_emissions.R")
compare_emissions(".")
```
