---
title: "dplyr wrangling"
output: html_document
---

```{r setup, include=FALSE}
reticulate::use_condaenv("r-codecarbon", required = TRUE)
```

## Workload

A short-running, CPU-only, small in-memory data wrangling pipeline. No
CodeCarbon example to mirror directly (its own examples are ML-focused),
so this is paired against an equivalent pandas pipeline instead. Generates
a synthetic 200,000-row sales table, then runs a
group_by/summarize/join/pivot chain: aggregate revenue by region and
category, join in a small tax-rate lookup table, then pivot categories out
into columns. R side uses `dplyr`/`tidyr`, Python side uses pandas
groupby/merge/pivot doing the same transformations.

As with case 01, the two languages' RNGs aren't bit-compatible, so the
generated data isn't identical between sides, just the same shape and
distribution; this validates that reported numbers are in a sane range
for a wrangling-shaped workload, not an exact duration match.

## R run

```{r}
library(CodeCarbonR)
library(dplyr)
library(tidyr)

set.seed(42)
n <- 200000
regions <- c("North", "South", "East", "West")
categories <- c("Electronics", "Grocery", "Apparel", "Home")

sales <- data.frame(
  region = sample(regions, n, replace = TRUE),
  category = sample(categories, n, replace = TRUE),
  quantity = sample(1:10, n, replace = TRUE),
  price = round(runif(n, 5, 500), 2)
)
tax_rates <- data.frame(
  region = regions,
  tax_rate = c(0.07, 0.06, 0.08, 0.075)
)

result <- with_emissions_tracked(
  {
    summary <- sales %>%
      group_by(region, category) %>%
      summarise(
        total_revenue = sum(quantity * price),
        avg_price = mean(price),
        n_orders = n(),
        .groups = "drop"
      ) %>%
      inner_join(tax_rates, by = "region") %>%
      mutate(revenue_after_tax = total_revenue * (1 - tax_rate))

    wide <- summary %>%
      select(region, category, total_revenue) %>%
      pivot_wider(names_from = category, values_from = total_revenue)

    wide
  },
  country_iso_code = "USA",
  output_dir = "r_output"
)

print(result$result)
result
```

## Python run

```{python}
import os
import numpy as np
import pandas as pd
from codecarbon import OfflineEmissionsTracker

os.makedirs("py_output", exist_ok=True)

np.random.seed(42)
n = 200_000
regions = ["North", "South", "East", "West"]
categories = ["Electronics", "Grocery", "Apparel", "Home"]

sales = pd.DataFrame({
    "region": np.random.choice(regions, n),
    "category": np.random.choice(categories, n),
    "quantity": np.random.randint(1, 11, n),
    "price": np.round(np.random.uniform(5, 500, n), 2),
})
tax_rates = pd.DataFrame({
    "region": regions,
    "tax_rate": [0.07, 0.06, 0.08, 0.075],
})

with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
    sales["revenue"] = sales["quantity"] * sales["price"]
    summary = (
        sales.groupby(["region", "category"])
        .agg(
            total_revenue=("revenue", "sum"),
            avg_price=("price", "mean"),
            n_orders=("revenue", "size"),
        )
        .reset_index()
        .merge(tax_rates, on="region")
    )
    summary["revenue_after_tax"] = summary["total_revenue"] * (1 - summary["tax_rate"])

    wide = summary.pivot(index="region", columns="category", values="total_revenue")

print(wide)
```

## Comparison

```{r}
source("../_harness/compare_emissions.R")
compare_emissions(".")
```
