---
title: "dplyr wrangling"
output: html_document
---

```{r setup, include=FALSE}
reticulate::use_condaenv("r-codecarbon", required = TRUE)
```

## Workload

TODO: a short-running, CPU-only, small in-memory data wrangling pipeline.
No CodeCarbon example to mirror directly; paired against an equivalent
pandas pipeline. Candidate workload: read a small CSV (or built-in
dataset), group_by/summarize/join/pivot chain, compare against pandas
groupby/merge/pivot doing the same transformations.

## R run

```{r}
# library(CodeCarbonR)
# library(dplyr)
#
# result <- with_emissions_tracked(
#   {
#     # wrangling pipeline
#   },
#   country_iso_code = "USA",
#   output_dir = "r_output"
# )
```

## Python run

```{python}
# import pandas as pd
# from codecarbon import OfflineEmissionsTracker
#
# with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
#     pass  # wrangling pipeline
```

## Comparison

```{r}
# source("../_harness/compare_emissions.R")
# compare_emissions(".")
```
