---
title: "gpu neural net"
format: html
---

## Workload

TODO: the GPU case, run on a cloud GPU instance rather than local hardware
(confirm instance type/provider before building this out). Needs a
framework decision: R `torch` package vs. Python PyTorch, or R `keras3` vs.
Python TensorFlow/Keras. Train a small neural net for enough epochs that
GPU utilization is sustained long enough for codecarbon's GPU sampling
(via `pynvml`/`nvidia-smi`) to register meaningfully.

Open question to confirm before building: does codecarbon's GPU tracking
path work identically when called from R via reticulate as it does from
native Python, or does anything about the reticulate boundary interfere
with `pynvml` access? This case is as much about testing that as about the
emissions numbers.

## R run

```{r}
# library(CodeCarbonR)
#
# result <- with_emissions_tracked(
#   {
#     # neural net training loop
#   },
#   country_iso_code = "USA",
#   output_dir = "r_output"
# )
```

## Python run

```{python}
# from codecarbon import OfflineEmissionsTracker
#
# with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
#     pass  # equivalent neural net training loop
```

## Comparison

```{r}
# source("../_harness/compare_emissions.R")
# compare_emissions(".")
```
