---
title: "gpu neural net"
output: html_document
---

```{r setup, include=FALSE}
reticulate::use_condaenv("r-codecarbon", required = TRUE)
```

## Workload

**Status: built, not yet validated.** This case needs an actual GPU
(ideally a cloud instance) to run meaningfully; the dev/CI environments
this suite has been exercised in so far are CPU-only. The code below is
complete and will run on CPU as a correctness check (falls back
automatically), but that does not exercise what this case exists to test.
Run it once on real GPU hardware and update `../coverage_matrix.md` to
`validated` before relying on it for the paper's cross-platform claims.

Framework: R `torch` vs Python `PyTorch`, not `keras3`/TensorFlow.
`torch` in R binds directly to libtorch, the same C++ library PyTorch
itself binds to, rather than routing through a separate Python backend
via reticulate the way `keras3` would -- so this keeps the R and Python
sides as two independent bindings to the same underlying engine, the same
spirit as case 01 pairing `ranger` against `scikit-learn` rather than
having one side call the other.

Trains a small feedforward network (2 hidden layers) on synthetic
regression data for 200 epochs, meant to be enough sustained GPU
utilization for codecarbon's GPU sampling (`pynvml`/`nvidia-smi`) to
register meaningfully -- increase `epochs` if a real run shows GPU power
draw isn't registering above noise.

Open question this case is meant to answer, not just the emissions
numbers: does codecarbon's GPU tracking path work identically when called
from R via `reticulate` as it does from native Python, or does anything
about the reticulate boundary interfere with `pynvml` access? Watch the
`gpu_power`/`gpu_energy` columns in `r_output/emissions.csv` specifically
for that.

## R run

```{r}
library(CodeCarbonR)
library(torch)

set.seed(42)
device <- if (cuda_is_available()) "cuda" else "cpu"

n <- 5000
p <- 50
x <- torch_randn(n, p)
true_w <- torch_randn(p, 1)
y <- x$matmul(true_w) + torch_randn(n, 1) * 0.1
x <- x$to(device = device)
y <- y$to(device = device)

model <- nn_sequential(
  nn_linear(p, 64), nn_relu(),
  nn_linear(64, 32), nn_relu(),
  nn_linear(32, 1)
)$to(device = device)

optimizer <- optim_adam(model$parameters, lr = 0.001)

result <- with_emissions_tracked(
  {
    for (epoch in seq_len(200)) {
      optimizer$zero_grad()
      pred <- model(x)
      loss <- nnf_mse_loss(pred, y)
      loss$backward()
      optimizer$step()
    }
    as.numeric(loss$item())
  },
  country_iso_code = "USA",
  output_dir = "r_output"
)

cat("Device:", device, "\n")
cat("Final training loss:", round(result$result, 4), "\n")
result
```

## Python run

```{python}
import os
import torch
import torch.nn as nn
from codecarbon import OfflineEmissionsTracker

os.makedirs("py_output", exist_ok=True)
torch.manual_seed(42)
device = "cuda" if torch.cuda.is_available() else "cpu"

n = 5000
p = 50
X = torch.randn(n, p)
true_w = torch.randn(p, 1)
y = X @ true_w + torch.randn(n, 1) * 0.1
X = X.to(device)
y = y.to(device)

model = nn.Sequential(
    nn.Linear(p, 64), nn.ReLU(),
    nn.Linear(64, 32), nn.ReLU(),
    nn.Linear(32, 1),
).to(device)

optimizer = torch.optim.Adam(model.parameters(), lr=0.001)
loss_fn = nn.MSELoss()

with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
    for epoch in range(200):
        optimizer.zero_grad()
        pred = model(X)
        loss = loss_fn(pred, y)
        loss.backward()
        optimizer.step()

print(f"Device: {device}")
print(f"Final training loss: {loss.item():.4f}")
```

## Comparison

```{r}
source("../_harness/compare_emissions.R")
compare_emissions(".")
```
