---
title: "multi step tracking"
output: html_document
---

```{r setup, include=FALSE}
reticulate::use_condaenv("r-codecarbon", required = TRUE)
```

## Workload

Exercises `carbon_tracker()$start()`/`$stop()` across three phases in one
script, rather than `with_emissions_tracked()`'s single-block path. Mirrors
the "Multiple Trackers" pattern from CodeCarbon's own docs:
https://docs.codecarbon.io/latest/how-to/scikit-learn/#multiple-trackers.

Reuses the random forest workload from case 01, split into three phases so
each is measured separately: data generation, training, and prediction.

Each phase gets its own tracker instance rather than reusing one instance's
`start()`/`stop()` across all three. Reuse doesn't work: `codecarbon`'s
`stop()` never resets its internal `_start_time`, so a `start()` after a
`stop()` on the same instance logs "Already started tracking" and no-ops,
and the following `stop()` logs "Tracker already stopped !" and returns the
first phase's emissions/energy figures again, frozen, with only `duration`
still climbing (measured from the original start). Confirmed identically on
both the R and raw Python side, so it's `codecarbon`'s tracker semantics,
not a CodeCarbonR wrapper bug. One tracker per phase is what actually
produces independent per-phase numbers, and matches what "Multiple
Trackers" in CodeCarbon's own docs means. Each `stop()` call still appends
one row to `emissions.csv` on both sides, so this still exercises the
repeated-append path of the output file.

## R run

```{r}
library(CodeCarbonR)
library(ranger)

set.seed(42)

tracker1 <- carbon_tracker(
  country_iso_code = "USA",
  project_name = "CodeCarbonR",
  output_dir = "r_output"
)
tracker1$start()
n <- 1000
p <- 20
x <- matrix(rnorm(n * p), nrow = n)
beta <- rnorm(p)
linpred <- x %*% beta
y <- factor(ifelse(linpred + rnorm(n) > median(linpred), 1, 0))
data <- as.data.frame(x)
data$y <- y
train_idx <- sample(seq_len(n), size = 0.8 * n)
train_data <- data[train_idx, ]
test_data <- data[-train_idx, ]
data_generation_emissions <- tracker1$stop()

tracker2 <- carbon_tracker(
  country_iso_code = "USA",
  project_name = "CodeCarbonR",
  output_dir = "r_output"
)
tracker2$start()
model <- ranger(y ~ ., data = train_data, num.trees = 100)
training_emissions <- tracker2$stop()

tracker3 <- carbon_tracker(
  country_iso_code = "USA",
  project_name = "CodeCarbonR",
  output_dir = "r_output"
)
tracker3$start()
predictions <- predict(model, test_data)$predictions
accuracy <- mean(predictions == test_data$y)
prediction_emissions <- tracker3$stop()

cat("Model accuracy:", round(accuracy, 3), "\n")
```

## Python run

```{python}
import os
from sklearn.datasets import make_classification
from sklearn.model_selection import train_test_split
from sklearn.ensemble import RandomForestClassifier
from codecarbon import OfflineEmissionsTracker

os.makedirs("py_output", exist_ok=True)

tracker1 = OfflineEmissionsTracker(
    country_iso_code="USA",
    project_name="CodeCarbonR",
    output_dir="py_output",
)
tracker1.start()
X, y = make_classification(n_samples=1000, n_features=20, random_state=42)
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2, random_state=42)
data_generation_emissions = tracker1.stop()

tracker2 = OfflineEmissionsTracker(
    country_iso_code="USA",
    project_name="CodeCarbonR",
    output_dir="py_output",
)
tracker2.start()
model = RandomForestClassifier(n_estimators=100, random_state=42)
model.fit(X_train, y_train)
training_emissions = tracker2.stop()

tracker3 = OfflineEmissionsTracker(
    country_iso_code="USA",
    project_name="CodeCarbonR",
    output_dir="py_output",
)
tracker3.start()
accuracy = model.score(X_test, y_test)
prediction_emissions = tracker3.stop()

print(f"Model accuracy: {accuracy:.3f}")
```

## Comparison

`compare_emissions_multi()` compares all three phases row by row, since
each tracker's `stop()` appends a new row to `emissions.csv` on both sides
in the same order the trackers were run.

```{r}
source("../_harness/compare_emissions.R")
compare_emissions_multi(".", phase_labels = c("data_generation", "training", "prediction"))
```
