---
title: "multi step tracking"
format: html
---

## Workload

Exercises `carbon_tracker()$start()`/`$stop()` directly across three
phases in one script, rather than `with_emissions_tracked()`'s single-block
path. Mirrors the "Multiple Trackers" pattern from CodeCarbon's own docs:
https://docs.codecarbon.io/latest/how-to/scikit-learn/#multiple-trackers.

TODO: pick the three phases. Candidate: reuse the random forest workload
from case 01, split into data generation / training / prediction phases,
each measured separately.

## R run

```{r}
# library(CodeCarbonR)
#
# tracker <- carbon_tracker(country_iso_code = "USA", output_dir = "r_output")
#
# tracker$start()
# # phase 1
# phase_1_emissions <- tracker$stop()
#
# tracker$start()
# # phase 2
# phase_2_emissions <- tracker$stop()
#
# tracker$start()
# # phase 3
# phase_3_emissions <- tracker$stop()
```

## Python run

```{python}
# from codecarbon import OfflineEmissionsTracker
#
# tracker = OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output")
#
# tracker.start()
# # phase 1
# phase_1_emissions = tracker.stop()
#
# tracker.start()
# # phase 2
# phase_2_emissions = tracker.stop()
#
# tracker.start()
# # phase 3
# phase_3_emissions = tracker.stop()
```

## Comparison

```{r}
# note: compare_emissions() as written compares the last row of each CSV,
# which only covers phase 3. Multi-phase comparison needs a small
# extension to compare all three rows, or three separate calls against
# row-sliced CSVs.
```
