---
title: "monte carlo simulation"
output: html_document
---

```{r setup, include=FALSE}
source("../_harness/use_r_codecarbon.R")
use_r_codecarbon()
```

## Workload

The long-running case: a loop-heavy stochastic simulation (8,000,000
iterations), estimating pi by the classic Monte Carlo circle/square ratio.
Deliberately written as an explicit `for` loop rather than vectorized code
on both sides, since a vectorized version would finish in well under a
second and defeat the point of this case: a workload with negligible
memory footprint (a couple of scalars) but sustained CPU work, to isolate
CPU-time-driven emissions from the data-size-driven emissions the other
cases exercise.

Neither side overrides `measure_power_secs` (codecarbon's default is 15s),
so this is also the case that actually exercises the tracker's periodic
background sampling more than once, unlike the sub-second cases elsewhere
in this suite where the reported figures come entirely from the
start/stop bookend measurement.

R's interpreted `for` loop is markedly slower per iteration than Python's
(measured ~9x on this machine: ~4.1us vs ~0.45us per iteration), so with
the same iteration count on both sides, expect R's `duration` to run
several times longer than Python's, same as the caveat in case 01. That's
expected here too, not a bug: the workload runs a comparable amount of
*work* (one random-point-in-circle test per iteration) but not comparable
wall-clock time, since the two interpreters aren't equally fast at that
same loop-based work.

## R run

```{r}
library(CodeCarbonR)

set.seed(42)
n <- 8000000

result <- with_emissions_tracked(
  {
    inside <- 0L
    for (i in seq_len(n)) {
      x <- runif(1, -1, 1)
      y <- runif(1, -1, 1)
      if (x * x + y * y <= 1) inside <- inside + 1L
    }
    4 * inside / n
  },
  country_iso_code = "USA",
  output_dir = "r_output"
)

cat("Pi estimate:", round(result$result, 4), "\n")
result
```

## Python run

```{python}
import os
import random
from codecarbon import OfflineEmissionsTracker

os.makedirs("py_output", exist_ok=True)
random.seed(42)
n = 8_000_000

with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
    inside = 0
    for _ in range(n):
        x = random.uniform(-1, 1)
        y = random.uniform(-1, 1)
        if x * x + y * y <= 1:
            inside += 1
    pi_estimate = 4 * inside / n

print(f"Pi estimate: {pi_estimate:.4f}")
```

## Comparison

```{r}
source("../_harness/compare_emissions.R")
compare_emissions(".")
```
