---
title: "monte carlo simulation"
output: html_document
---

```{r setup, include=FALSE}
reticulate::use_condaenv("r-codecarbon", required = TRUE)
```

## Workload

TODO: the long-running case. A loop-heavy stochastic simulation (thousands
to millions of iterations, e.g. a bootstrap or random-walk process) with
negligible memory footprint, to isolate CPU-time-driven emissions from
data-size-driven emissions. Needs a target runtime decided (a few minutes,
long enough that tracker sampling interval doesn't dominate the
measurement).

## R run

```{r}
# library(CodeCarbonR)
#
# result <- with_emissions_tracked(
#   {
#     # simulation loop
#   },
#   country_iso_code = "USA",
#   output_dir = "r_output"
# )
```

## Python run

```{python}
# from codecarbon import OfflineEmissionsTracker
#
# with OfflineEmissionsTracker(country_iso_code="USA", output_dir="py_output") as tracker:
#     pass  # equivalent simulation loop
```

## Comparison

```{r}
# source("../_harness/compare_emissions.R")
# compare_emissions(".")
```
